Multi-Objective Optimization in Image Approximation \\ {} \thanks{The publication has been prepared with the support of Velbazhd Software LLC and Bulgarian Ministry of Education and Science according to the research project No. {D01–205/23.11.2018}.}

### 2020-06-28 Multiobjective-Optimization-in-Image-Approximation/paper.tex
Almost all of the main text was written.

\title{Multiobjective Optimization in Image Approximation \\ {}
\thanks{The publication has been prepared with the support of Velbazhd Software LLC and Bulgarian Ministry of Education and Science according to the research project No. {D01–205/23.11.2018}.}}

@@

Packing problems are well known in geometry from centuries. The goal is to pack certain objects into a container. The most popular case of this problem is when a single container should be filled as dense as possible \cite{Lodi-Martello-Monaci-2002}. There is a dualism for each packing problem as a covering problem. In covering problems it is asked how many objects are required in such organization that will cover the most area in the container. This problem is defined in two cases where object can or can not overlap. The most popular problems in two-dimensional space are: Packing circles in a circle \cite{Fodor-2003}; Packing circles in a square \cite{Huang-Ye-2010}; Packing circles in an isosceles or right triangle \cite{Xu-1996}; Packing circles an equilateral triangle \cite{Nurmela-2000}; Packing squares in a square \cite{Stromquist-2003}.

@@

Some visualization devices are not capable to handle a high number of colors. This is the case with 2D plotting machines. They have limited number of different colors. Also, different colors are handled consequently. It means that the device is doing only a single color in time. The other very important feature of the plotting devices is that they are operating with graphical primitives (lines, arcs, and other simple shapes). Such handling of the visual information is pretty different than what is used in pixel-based devices. If a bitmap image should be visualized on a 2D plotting machine the bitmap image should be transformed in a set of instructions (usually G-Codes) and the number of colors should be drastically reduced. This process has two common components -  color reduction and vectorization.

@@

@@

@@

\begin{verbnobox}[\tiny]
java -jar Ellipses-Image-Approximator-all.jar -input ../../input/0001.jpg 
-output ~/Desktop/ -pixel_closest_color -g_code_print -g_code_comments 
-g_code_x_home 40 -g_code_y_home 90 -g_code_z_up 35 
-g_code_z_down 80 -g_code_width 80.0 -g_code_height 80.0 
-g_code_refill_count 3 -ellipse_width 19 -ellipse_height 5 -ellipse_alpha 216 
-colors FFFFFF,FFFF00,CC7722,E34234,DC143C,49796B,40826D,120A8F,
0000FF,E97451,635147,000000 -ga -ga_population_size 37 
-ga_tournament_arity 2 -ga_crossover_rate 0.95 -ga_mutation_rate 0.01 
-ga_elitism_rate 0.05 -ga_optimization_time 3600
\end{verbnobox}

@@

As further research, it will be challenging distributed genetic algorithms to be applied. In such implementation, the most time-consuming calculations would be done on different heterogeneous machines.

@@

@@

@@

@@

>>>>

\title{Multi-Objective Optimization in Image Approximation \\ {}
\thanks{The publication has been prepared with the support of Velbazhd Software LLC and Bulgarian Ministry of Education and Science according to the research project No. {D01–205/23.11.2018}.}}

@@

Packing problems are well known in geometry for centuries and there are even more relevant with the extensive development of soft computing \cite{Angelova-2009}. The goal is to pack certain objects into a container. The most popular case of this problem is when a single container should be filled as dense as possible \cite{Lodi-Martello-Monaci-2002}. There is a dualism for each packing problem as a covering problem. In covering problems it is asked how many objects are required in such organization that will cover the most area in the container. This problem is defined in two cases where object can or can not overlap. The most popular problems in two-dimensional space are: Packing circles in a circle \cite{Fodor-2003}; Packing circles in a square \cite{Huang-Ye-2010}; Packing circles in an isosceles or right triangle \cite{Xu-1996}; Packing circles an equilateral triangle \cite{Nurmela-2000}; Packing squares in a square \cite{Stromquist-2003}.

@@

Some visualization devices (IoT for example \cite{Dineva-Atanasova-2019}) are not capable to handle a high number of colors. This is the case with 2D plotting machines. They have limited number of different colors. Also, different colors are handled consequently. It means that the device is doing only a single color in time and proper job scheduling is needed \cite{Borissova-Mustakerov-2015}. The other very important feature of the plotting devices is that they are operating with graphical primitives (lines, arcs, and other simple shapes). Such handling of the visual information is pretty different than what is used in pixel-based devices. If a bitmap image should be visualized on a 2D plotting machine the bitmap image should be transformed in a set of instructions (usually G-Codes) and the number of colors should be drastically reduced. This process has two common components -  color reduction and vectorization.

@@

\subsection{Technical Implementation}

Ellipse with predefined width and height is selected as base 2D visual primitive for the approximation. Ellipse is appropriate because acrylic paint will be drawn with a small brush. It is accepted that each stroke with the brush will resemble an ellipse. Sharp lines or long rectangles are the other options, but they are less close to the shape of a single brush stroke. For simplicity in the current research, it is accepted that all ellipses are with identical sized. This can be elaborated on in some further researchers. Each ellipse is described with four numerical values - coordinates of the center (x and y values), angle of rotation around the center, and index of color from the provided list of colors.

A list of ellipses with variable size presents the genetic algorithm chromosome. The list of ellipses is sorted before fitness value calculation because the most frequent colors should be drawn first and the less frequent colors should be drawn last. Such a drawing organization is needed because ellipses are allowed to overlap and the most frequent once can completely cover the least frequent once. The length of the chromosomes can vary and it is one of the criteria put under optimization. If the approximated image can be drawn with less number of primitive objects it will reduce drawing time (operating efficiency) and paint consumption (cost efficiency).

The exploration part of genetic algorithms is done with the crossover operator. With chromosomes as lists of ellipses uniform crossover perfectly fits the need of exploration. Getting elements from parent chromosomes is organized in such way that children can be produced with different lengths. The exploitation part of genetic algorithms is done with the mutation operator. In this research randomly selected ellipse from the child chromosome is randomly changed as coordinates of the center, rotation angle, and color index. The trade-off between exploration and exploitation in genetic algorithms affects the completeness of wide optimization space investigation and near sub-optimal solutions investigation \cite{Hussain-Muhammad-2020}.

The first component in the multi-objective fitness function is the closeness between the original bitmap image and the approximated bitmap image. As smaller is the difference between the both images as better is the sub-optimal solution. For this objective minimum is desired as sub-optimality. For the calculation of closeness, the original bitmap is taken unmodified. The approximated image on the other side is generated by drawing of all chromosome's ellipses in a bitmap image. Both images have identical dimensions. In the current research, the average Euclidean distance between the pixels in the images is calculated. Such a measure of image similarity is not accurate enough. It does not take into account image composition. In some further research, it will be better some kind of hierarchical granularity to be involved.

The second component in the multi-objective fitness function is the total amount of blank area. The perfect case for this objective is when there is no blank area. As with the previous objective, the minimum is desired for better sub-optimality. The amount of blank area is easily calculated by filling the initial drawing area of the approximated image with a certain value of transparency. The amount of blank area is the count of the pixels which remain unchanged after ellipses drawing.

The third component in the multi-objective fitness function is the count of drawn ellipses. It is obvious that less number of ellipses will faster produce a picture with less paint usage. As with the previous two objectives, the minimum is desired as a better sub-optimality. This objective dramatically opposes the other two objectives. If the number of drawn ellipses is zero it will not cost time and it will not cost paint. The problem is that with zero ellipses images distancing will be high and the blank area will be the maximum possible.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{fig02.png}}
\caption{The result after the first run of the experiment.}
\label{fig02}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{fig03.png}}
\caption{The result after the second run of the experiment.}
\label{fig03}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{fig04.png}}
\caption{The result after the third run of the experiment.}
\label{fig04}
\end{figure}

@@

\begin{verbnobox}[\small]
java -jar Ellipses-Image-Approximator-all.jar 
-input ../../input/0001.jpg -output ~/Desktop/ 
-pixel_closest_color -g_code_print 
-g_code_comments -g_code_x_home 40 
-g_code_y_home 90 -g_code_z_up 35 
-g_code_z_down 80 -g_code_width 80.0 
-g_code_height 80.0 -g_code_refill_count 3 
-ellipse_width 19 -ellipse_height 5 
-ellipse_alpha 216 -colors FFFFFF,FFFF00,
CC7722,E34234,DC143C,49796B,40826D,
120A8F,0000FF,E97451,635147,000000 -ga 
-ga_population_size 37 -ga_tournament_arity 2 
-ga_crossover_rate 0.95 -ga_mutation_rate 0.01 
-ga_elitism_rate 0.05 -ga_optimization_time 3600
\end{verbnobox}

Three separate experiments were executed. As it is shown in Fig. \ref{fig02}-\ref{fig04}, the most informative elements of the bitmap image are kept in the approximated images. There are some deviations in the results, but it is expected because of the probabilistic nature of the genetic algorithms. The count of the ellipses used for the approximation is relatively acceptable, but the presence of obvious blank areas is not of the desired amount.

@@

As further research, it will be challenging distributed genetic algorithms to be applied. In such implementation, the most time-consuming calculations would be done on different heterogeneous machines or on a single supercomputer as AVITOHOL \cite{Tashev-Tasheva-Petrov-2019}.

@@

\bibitem{Angelova-2009} V. Angelova, ``Investigations in the Area of Soft Computing Targeted State of the Art Report'', Cybernetics and Information Technologies, vol. 9, no. 1, 2009, pp. 18--24.

@@

\bibitem{Dineva-Atanasova-2019} K. Dineva, T. Atanasova, ``Methodology for Data Processing in Modular IoT System'', Distributed Computer and Communication Networks, Proceedings of 22-st International Conference, Springer Nature Switzerland, vol. 11965, 2019, pp. 457--468.

\bibitem{Borissova-Mustakerov-2015} D. Borissova, I. Mustakerov, ``Open job shop scheduling via enumerative combinatorics'', International Journal of Mathematical Models and Methods in Applied Sciences, vol. 9, 2015, pp. 120--127.

@@

\bibitem{Hussain-Muhammad-2020} A. Hussain, Y.S. Muhammad, ``Trade-off between exploration and exploitation with genetic algorithm using a novel selection operator'', Complex \& Intelligent Systems, vol. 6, 2020, pp. 1--14.

@@

\bibitem{Tashev-Tasheva-Petrov-2019} T. Tashev, R. Tasheva, P. Petrov, ``Determination of the Computer Modelling Precision for Throughput of Switch Node with LPF-algorithm'', Proceedings of  International Conference on Computer Systems and Technologies, ACM, 2019, pp. 141--145.
